The \frb\ Campaign, a Multi-Telescope Burst Detection, and Implications for the FRB Population

### 2017-03-24 repeater-vladata.tex
ready to distribute!

\title{The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

@@

\begin{abstract}
The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source. We present results of the coordinated observing campaign that made this localization, including the first simultaneous detection of an FRB burst with multiple telescopes. Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz. We show that the burst spectra typically have a $\sim500$~MHz-scale envelope, plus fine spectral structure on MHz-frequency scales. We also calculate the energy distribution and temporal statistics for \frb...
%\ and argue that the whole FRB population is adequately described by a single class similar to \frb. 
*population models* *slsn*
**This source shows that optimal FRB survey strategies should...**
\end{abstract}

@@

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec. Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01" \citep[$\sim40$\ pc]{OPT, EVN}.

@@

Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them. 
**magnetar birth?**
Its coincidence with a compact, persistent radio source is consistent with \frb as a young magnetar powering a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}. It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments.
Also, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.

We can also assume that \frb\ is representative of all FRBs and use it to constrain the physical processes at play in the overall FRB population. In this case, we know that FRBs are apparently luminous, but if that is due to intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}. The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

This paper opens by describing the multi-telescope observing campaign and a refined analysis of the nine VLA bursts. Next, we present the spectrum of a burst from \frb\ that was simultaneously detected by the VLA and Arecibo observatories. **Simulations of temporal statistics and luminosity distribution...** **New estimate of FRB rate and comparison to other transient populations** We close with a discussion of how the \frb\ burst spectra, host properties, burst rate estimates, and other properties inform new strategies for finding FRBs.

@@

\subsection{VLA}
The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration. In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo. We concluded with a 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration. In the late-2016 campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz. This paper focuses on the data collected at 3~GHz, which includes all nine burst detections and is the widest bandwidth to have ever detected an FRB.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}. The channel frequency width was set to maximize sensitivity to the known DM of \frb with the largest total bandwidth. The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in eight spectral windows with 32 channels each.

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}. Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}. Gain calibration was made from observations of J0555+3948 by the ``telcal'' system, which uses phase-only calibration. A flux scale is calculated for each spectral window from an observation on {\color{red}xx (Bryan)} and applied to all burst spectra.

@@

Effelsberg observations were conducted with the S60mm receiver at an observing frequency of 4.6 to 5.1~GHz. Total intensity spectra were recorded by the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s and 128 frequency channels. The system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin at 4.85~GHz.

@@

\subsection{Multi-Observatory Burst Spectrum}
Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}). Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo). The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$ with integrated flux densities of 111 mJy and 14 mJy, respectively. Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha\approx2.7$.

@@

\subsubsection{Spectral Modeling}
\label{sec:spec}
This paper refine the analysis of the nine VLA radio burst spectra described in \citet{LOC} in a few ways. We use a better calibration scheme and have optimized the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[(RA, Dec) $=$ (05h31m58.70s, +33d08m52.5s);][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.

@@

While most bursts are modeled with well-defined parameter probability distributions, one burst is an outlier. Figure \ref{fig:corner} shows the scatterplot matrix for the MCMC run on burst 57646 \citep{corner}. Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM. The model seems to be too simple for this burst. This is consistent with high-resolution Arecibo burst spectra \citep{WEIRD}, which show that bursts are composed of "sub-bursts" that drift in frequency.

\subsubsection{Dispersion}
The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. 
%In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$. However, the uncertainty in the peak DM measurement is defined by the signal-to-noise of the burst and how this changes with DM.
The MCMC modeling is more sophsticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.

@@

\subsection{Temporal Statistics}
\label{sec:temp}
The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \cite{fig:multi}). In the early-2016 campaign, we observed for 30 hours at S-band and no bursts were detected. In the late-2016 observing campaign, nine bursts were detected in the last 27 hours of S-band observing. Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary. Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit). The S-band burst rate was much higher during the late-2016 campaign, $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.

%There is weak evidence that the \frb\ burst rate decreased through the S-band observing in the late-2016 campaign. We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$. By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence. This weak constraint is consistent with the broader trend of a changing rate seen on month timescales by Arecibo.
%
%\begin{figure}[htb]
%\begin{center}
%\includegraphics[width=0.9\columnwidth]{event_rate_contours}
%\caption{Color scale and contours show the relative probability for a time-evolving Poisson detection probability for \frb. Contours show the 50, 90, and 95\% confidence contours on the rate $a$\ (bursts s$^{-1}$) and rate change $b$\ (bursts s$^{-1}$ day$^{-1}$) during the August--September 2016 campaign in which bursts were detected.
%\label{fig:rate}}
%\end{center}
%\end{figure}
%
%During the late-2016 observing campaign, the typical observation lasted about two hours and was sampled with a 5~ms cadence. We used the Lomb-Scargle periodogram \citep{1982ApJ...263..835S} to search for periodic structure over a wide range of timescales. The time series is calculated by binning the burst detection rate per 100~ms \citep[always either 0 or 1, see also][]{2011MNRAS.417.1871P}. 
%The spectral power calculated for periods between 0.8 and 80 s shows no power in excess of the typical 95\% confidence bound estimated from shuffled data. We verified that simulating nine bursts drawn from a simple rotational model would produce excess power using this approach. However, it is difficult to put strong constraints on more complex rotational models \citep[e.g., with wide pulse phase windows or glitches;][]{2007ApJ...663..497C, 2013Natur.497..591A}

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}). Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band. Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.

Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution as seen by the VLA and calculated from prior observations by Arecibo and the GBT \citep{2016Natur.531..202S,2016arXiv160308880S}. The latter two energy distributions are scaled from the fluence by assuming that all burst energy is included by the observation. This likely underestimates the burst energy for some bursts by a factor of a few, but should not affect the slope of the distribution. The Arecibo and GBT energies were scaled by factors of {\color{red} 2 and 1 (help)}, respectively, to correct for the sensitivity loss due to the primary beam.

@@

%\subsubsection{Spectral Autocorrelation}
%\label{sec:auto}
%Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}. Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68). The is no strong excess correlation near the channel resolution, which limits the correlation width to less than roughly 4~MHz. This is broadly consistent with expectations of Galactic diffractive scintillation bandwidth \citep[3--9~MHz near 3~GHz][]{2002astro.ph..7156C}.
%
%**Does channel-scale structure only appear around 3~GHz?**
%
%\begin{figure}[htb]
%\begin{center}
%\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
%\caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68. The largest black dots show the autocorrelation for the data, smaller dots show the autocorrelation for the best Gaussian model, and dashed line shows the autocorrelation of an off-burst spectrum.
%\label{fig:acf}}
%\end{center}
%\end{figure}

@@

After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift. This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$. We also measure a burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts of a similar scale. This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this ''excess'', burst-specific DM is seen up to 3~GHz. The simultaneous VLA/Arecibo burst also shows that an individual burst's properties from 1.2 to 3.5~GHz are consistent with a single excess.

These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}. That work uses bright, coherently-dedispersed bursts to identify ''sub-bursts'' that preferentially drift to lower frequencies at later times. With high-resolution dynamic spectra, one can define a heuristic that distinguishes between a burst-specific dispersion-like effect and a more stable (''true'') dispersion. Since the sub-bursts tend to drift to lower frequencies, they systematically bias DM measurements made with low-resolution data (like the VLA and earlier Arecibo and GBT obsrevaitons). Interestingly, our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width. This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum.

@@

While the surprising brightness of new FRB discoveries was once seen as a cause for concern (i.e., a sign of terrestrial interference), we may be able to use this to infer properties of the overall population \citep{2007Sci...318..777L, 2016arXiv161105758R}. When modeling the flux distribution as a powerlaw, an isotropic distribution of sources will have a powerlaw index, $\alpha$, of --1.5 \citep[the ''Euclidean distribution'';][]{2016MNRAS.462..941L}. Prior to the measurement of the first GRB redshift, deviations from the Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}. Multiple studies have suggested that FRBs have a ''flat'' flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. Others have noted that the flux distribution is not well modeled as a powerlaw, such that $\alpha$\ is effectively sensitivity (and telescope) dependent \citep{2016MNRAS.461..984O, 2017arXiv170208040C}.

We now know that \frb\ is detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population. \citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (''k-correction'') effects can flatten the flux distribution. To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice. Rather than using wide band burst spectra to measure a single ''typical'' spectral index, we now must measure the burst rate as a function of frequency. These need not be measured simultaneously, but rather contemporaneously to insure they represent a similar state of activitity of the FRB.

@@

%While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb is detectable \citep[e.g.,][]{2010ApJ...709..644I}. The burst energies are estimated from observations from 2.5 to 3.5~GHz, which may be a biased selection of all bursts or may not include all burst emission. If the simulation is revealing a connection between \frb and the broader FRB population, it does not explain the physical mechanism that drives it. The burst energy distribution of the population could be dominated by intrinsic or extrinsic effects \citep{2015MNRAS.451.3278M,2016Natur.531..202S,CORDES}. More FRB detections will improve the quality of this inference as sample variance drops, while more burst detetions from \frb\ will improve the measurement of the intrinsic energy distribution.

@@

The chance of detecting a burst with the VLA changes substantially on day--month timescales. A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects \citep{CORDES}. However, the temporal distribution of VLA detections alone shows that \frb\ has significant correlation on short timescales. That is, detecting a burst predicts you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likey not detect another burst soon thereafter. While this is sometimes referred to as a ''red spectrum'' \citep{2016MNRAS.458L..89C}, the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).

If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}. It is possible that other FRBs have repeating bursts, but calculating a limit requires knowing their temporal correlation function. Wide, shallow surveys are the preferred strategy for blind detection of FRBs. Also, since ''bursts predict bursts'', many short observations are more likely to blindly detect an FRB than a single long observation of the same total length.

@@

\section{Conclusions}
Prior to being established as a cosmological source, the low Galactic latitude of \frb\ made it a somewhat compromised member of the FRB class. With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined. That fact, combined with an abundance of data collected during its high activity state, allows us to think more generally about the physics of broader FRB population.

We presented the first multi-telescope detection (Arecibo and VLA) of an FRB. By detecting this burst from 1.2 to 4.5~GHz, we have demonstrated that some bursts have broad spectral structure. However, three other VLA bursts are undetected by Arecibo. That, combined with the measurement of spectra within the VLA band, suggest that the typical burst has a characteristic Gaussian spectral shape with width $\sim500$\ MHz.

**Flux/lum distribution**

>>>>

\title{The \frb\ Campaign, a Multi-Telescope Burst Detection, and Implications for the FRB Population}
\shorttitle{\frb\ Observing Campaign}
\shortauthors{Law et al.}

@@

\begin{abstract}
We present results of the coordinated observing campaign that made the first localization of a Fast Radio Burst, FRB 121102. Of the nine bursts detected by the Very Large Array at 3~GHz, four had simultaneous observing coverage at other observatories, and one was detected by the Arecibo Observatory at 1.4~GHz. We use this simultaneous detection, plus modeling of bursts only seen at 3~GHz to show that burst spectra are not well characterized by a powerlaw. Instead, bursts typically have a $\sim500$~MHz-scale envelope and total energies as high as $10^{40}$\ erg. The dispersion measure apparently changes significantly ($\sim5$\ pc cm$^{-3}$) between bursts, which suggests that they have intrinsic spectral structure that can bias the estimate of DM.
We use \frb\ as a prototype of the FRB class to estimate the first flux-independent volumetric rate of $R_{\rm{FRB}} \approx 5\times10^{-5}$\ Mpc$^{-3}$\ yr$^{-1}$ for the cosmic volume out to redshift of 1. This rate is broadly consistent with models of FRBs from young magnetars or fast pulsars, if the typical FRB repeats on the order of $10^3$\ times in its life.
\end{abstract}

@@

This paper is part of a series based on the first localization of an FRB and its unambiguous association to an extragalactic host \citep{LOC, OPT, EVN}. \frb, also known as the ``repeating FRB'', was first detected in November 2012 by the Arecibo Observatory \citep{2014ApJ...790..101S}. In mid 2015, new Arecibo observations revealed a series of bursts at the same DM ($\sim559$\ pc cm$^{-3}$) and sky position demonstrating that it repeats \citep{2016Natur.531..202S}. Beginning in August of 2015, we made the first of nine detections of \frb\ with the Very Large Array \citep{LOC} and localized it with a precision of 0.1\arcsec. Subsequent radio and optical observing discovered more bursts from \frb\ and associated them with a persistent radio and optical source at a redshift of 0.193 with a precision of 0.01\arcsec \citep[$\sim40$\ pc]{OPT, EVN}.

@@

Although new models of FRB origin have been already been developed \citep{2017arXiv170104815K, 2017arXiv170102370M, 2017arXiv170104094Z, 2017arXiv170102492D}, we still do not know what causes them. Its coincidence with a compact, persistent radio source is consistent with \frb\ as a young magnetar powering a luminous pulsar wind nebula \citep{2017arXiv170104815K}. At the same time, \frb\ is found in a low-metallicity dwarf galaxy, which is the preferred environment for long GRBs and Type-I superluminous supernovae \citep[LGRB and SLSN-I, respectively;][]{2017arXiv170102370M}. It has been suggested that these other classes of transient are signatures of the birth of magnetars that are only born in low-metallicity environments \citep{2014ApJ...787..138L}.

%Also, it has not been demonstrated that \frb\ is representative of the overall FRB population. In fact, the repetition of its bursts is unique among all FRBs \citep{2015MNRAS.454..457P}, so it is natural to ask whether \frb\ is representative. An important first step is to demonstrate that the properties of \frb\ are consistent with the significant body of facts for the overall population \citep{2015MNRAS.451.3278M, 2016MPLA...3130013K}. The repeating nature of \frb\ provides us with a sample of bursts covering a range of spectral properties, temporal properties, and luminosities that can be used to test its connection to the larger FRB population.

If we assume that \frb\ is representative of all FRBs, we use it to constrain the physical processes at play in the overall FRB population. We know that FRBs are apparently luminous, but more data is needed to distinguish between intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C} and extrinsic effects like scintillation \citep{CORDES}. The paper presents an analysis of the spectral properties of VLA bursts implied by simultaneous observing at Effelsberg, GBT, AMI-LA, and Arecibo, including the first simultaneous detection of an FRB at two observatories. The repetition of \frb\ also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

This paper opens by describing the multi-telescope observing campaign and a refined analysis of the nine VLA bursts. Next, we present the spectrum of a burst from \frb\ that was simultaneously detected by the VLA and Arecibo observatories. We then discuss modeling of the dynamic spectra that simultaneously considers the spectral and temporal evolution of the bursts. The burst temporal and energy distributions are presented and compared to those of bursts detected in earlier observing campaigns of \frb. We use the new properties defined for \frb\ to make the first flux-independent estimate of the FRB volumetric rate. Finally, we close with a discussion of how the \frb\ burst spectra, host properties, burst rate estimates, and other properties inform new strategies for finding FRBs.

@@

\subsection{VLA}

The \frb\ observing campaign started in late 2015 with a 10~hr campaign observed at 1.4~GHz in the compact D configuration. In April through May 2016, we conducted a 40~hr campaign at 3~GHz in the C and CnB configurations in coordination with Arecibo. We concluded with a 40~hr, coordinated campaign from August through September 2016 in the B configuration and during the move to the most extended A configuration. In the late-2016 campaign, the first 34 hours of VLA observations were made at 3~GHz, while the last 6 hours were observed at 6~GHz. This paper focuses on the data collected at 3~GHz, which includes all nine burst detections and is the widest bandwidth to have ever detected an FRB.

All VLA fast-sampled data were observed with 5~ms sampling, 256 channels, and dual-circular polarization \citep{2015ApJ...807...16L}. The channel frequency width was set to maximize sensitivity to the known DM of \frb\ with the largest total bandwidth. The total bandwidth at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands was 256~MHz, 1024~MHz, and 2048~MHz, respectively. The 3~GHz data were recorded data in eight spectral windows with 32 channels each.

Observations in August and September were searched by a prototype version of \rf\footnote{See \url{http://realfast.io}.}. \rf\ is a real-time, fast imaging transient search system. The current prototype runs on CPU-based hardware that is normally dedicated to the VLA correlator; for this experiment, it runs the transient search pipeline software called \emph{rtpipe} \citep[\url{https://github.com/caseyjlaw/rtpipe};][]{2015ApJ...807...16L}. Images were formed for each integration with a DM grid of 0, 546, 556.9, 560, and 565 pc cm$^{-3}$ and a time resampling grid of 5, 10, 20, 40, and 80 ms. This DM grid was chosen to maintain 90\% sensitivity to the nominal DM range of 540--570 pc cm$^{-3}$, which includes the known \frb\ DM of 559 pc cm$^{-3}$ \citep{2016arXiv160308880S}. Gain calibration was made from observations of J0555+3948 by the telcal system, which uses phase-only calibration. A flux scale is calculated for each spectral window from an observation of 3C48 and applied to all burst spectra.

@@

Effelsberg observations were conducted with the S60mm receiver at an observing frequency of 4.6 to 5.1~GHz. Total intensity spectra were recorded by the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s and 128 frequency channels. The system equivalent flux density is 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.

@@

\subsection{Multi-Observatory Burst Spectrum}

Four of the VLA bursts were observed simultaneously with Arecibo and AMI-LA, while two were observed simultaneously with all four observatories (Figure \ref{fig:multi}). Of these bursts, only one VLA burst (on MJD 57648) was simultaneously detected by another observatory (Arecibo). The VLA and Arecibo burst detections had significances of 25$\sigma$\ and 39$\sigma$\ with integrated flux densities of 111 mJy and 14 mJy, respectively. Assuming a powerlaw flux density model ($S_{\nu} \propto \nu^{\alpha}$), we find a spectral index $\alpha\approx2.7$.

@@

\subsubsection{Spectral Modeling}
\label{sec:spec}

This paper refine the analysis of the nine VLA radio burst spectra described in \citet{LOC} in a few ways. We use a better calibration scheme and have optimized the detection significance over a fine grid of DM ($\Delta \rm{DM}=1\ \rm{pc}\ \rm{cm}^{-3}$). After calibration and flagging, the visibility phases were rotated to the best-fit location \citep[(RA, Dec) $=$ (05h31m58.70s, +33d08m52.5s);][]{LOC} to extract a Stokes I spectrum that maximizes the image S/N for each burst.

@@

While most bursts are modeled with well-defined parameter probability distributions, one burst is an outlier. Figure \ref{fig:corner} shows the scatterplot matrix for the MCMC run on burst 57646 \citep{corner}. Two clusters of samples are identified for this burst: one narrow, low-DM and one wide, high-DM. The model seems to be too simple for this burst or that it can be decomposed into two bursts.

\subsubsection{Dispersion}

The initial VLA detections were made with a matched-filter approach that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta \rm{DM}=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. 
%In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$. However, the uncertainty in the peak DM measurement is defined by the signal-to-noise of the burst and how this changes with DM.
The MCMC modeling is more sophsticated in that it considers a wider range of parameters and models both data and observing effects (frequency-time pixel boundaries) simultaneously.

@@

\subsection{Temporal Statistics}
\label{sec:temp}

The burst rate for \frb\ varied dramatically throughout the 2016 observing campaign (Figure \ref{fig:multi}). In the early-2016 campaign, we observed for 30 hours at S-band and no bursts were detected. In the late-2016 observing campaign, nine bursts were detected in the last 27 hours of S-band observing. Overall, the data quality is uniform and high, so the inhomogeneous burst distribution shows that the burst detection probability was not stationary. Assuming that the burst detection probability follows a Poisson distribution, the nondetection in the first half of S-band limits the FRB rate to $\rm{R}<0.1$\ hour$^{-1}$\ (95\% confidence limit). The S-band burst rate was much higher during the late-2016 campaign, $\rm{R}=0.33\pm0.1$\ hour$^{-1}$.

\subsection{Energy and Brightness Distribution}
\label{sec:disn}

Knowing the source distance, we calculate the burst energy by integrating flux in time and frequency (Table \ref{tab:spec}). Some VLA burst spectra seem to be contained by the 2.5 to 3.5~GHz band and most of them seem to have Gaussian envelopes that are well modeled by the emission within that band. Assuming that the Gaussian shape defines the emission window, the mean S-band flux density can be converted to a total energy with no further assumptions about their spectral properties.

Figure \ref{fig:ed} shows the \frb\ burst energy cumulative distribution as seen by the VLA and calculated from prior observations by Arecibo and the GBT \citep{2016Natur.531..202S,2016arXiv160308880S}. The latter two energy distributions are scaled from the fluence by assuming that all burst energy is included by the observation. This likely underestimates the burst energy for some bursts by a factor of a few, but should not affect the slope of the distribution. The Arecibo and GBT energies were scaled by factors of {\color{red} 2 and 1 (anyone?)}, respectively, to correct for the sensitivity loss due to the primary beam.

@@

@@

After correcting for barycentric and typical dispersion delays, the VLA/Arecibo burst spectrum shows a residual temporal drift. This drift can be interpreted as an excess DM of roughly 5 pc cm$^{-3}$. We also measure a burst-to-burst variation in DM within the whole sample of VLA 3~GHz bursts of a similar scale. This variation had been noted in earlier 1.4~GHz Arecibo observations of \frb\ \citep{2016arXiv160308880S}, but the VLA bursts demonstrate that this burst-specific DM is seen up to 3~GHz. The simultaneous VLA/Arecibo burst also shows that an individual burst's properties from 1.2 to 3.5~GHz are consistent with a single excess.

These features are generally consistent with intrinsic burst properties described in \citet{WEIRD}. That work uses bright, coherently-dedispersed bursts to identify sub-bursts that preferentially drift to lower frequencies at later times. With high-resolution dynamic spectra, one can define a heuristic that distinguishes between a burst-specific dispersion-like effect and a more stable (``true'') dispersion. Since the sub-bursts tend to drift to lower frequencies, they systematically bias DM measurements made with low-resolution data (like the VLA and earlier Arecibo and GBT obsrevaitons). Interestingly, our modeling of the VLA burst dynamic spectra show a weak correlation between larger apparent DM and pulse width. This could be a signature of blending of many unresovled sub-bursts in a single VLA burst spectrum.

@@

While the surprising brightness of new FRB discoveries was once seen as a cause for concern (i.e., a sign of terrestrial interference), we may be able to use this to infer properties of the overall population \citep{2007Sci...318..777L, 2016arXiv161105758R}. When modeling the flux distribution as a powerlaw, an isotropic distribution of sources will have a powerlaw index, $\alpha$, of --1.5 \citep[the ``Euclidean distribution'';][]{2016MNRAS.462..941L}. Prior to the measurement of the first GRB redshift, deviations from the Euclidean distribution were used to infer their cosmological distribution \citep[e.g., the $V/V_{\rm{max}}$\ test;][]{1992ApJ...388L..45M, 1995ApJ...453...25F}. Multiple studies have suggested that FRBs have a sub-Euclidean flux distribution \citep[$-0.5<\alpha<-0.9$;][]{2016ApJ...830...75V, 2016arXiv160206099L, 2016arXiv161100458L}. Others have noted that the flux distribution is not well modeled as a powerlaw, such that $\alpha$\ is effectively sensitivity (and telescope) dependent \citep{2016MNRAS.461..984O, 2017arXiv170208040C}.

We now know that \frb\ is detectable with the VLA out to $z=0.7$, which suggests that cosmological effects are even more important for understanding properites of the FRB population. \citet{2017arXiv170208040C} demonstrate how redshift space distortions, time dilation, and spectral index (``k-correction'') effects can flatten the flux distribution. To this complex scene, we add the fact that \frb\ burst spectra are not defined by a spectral index, which suggests that k-corrections are likely to be very difficult to calculate in practice. Rather than using wide band burst spectra to measure a single spectral index, we now must measure the burst rate as a function of frequency. These need to be measured at similar times to insure they represent a similar state of activitity of the FRB.

@@

%While the \frb\ burst energy distribution is consistent with the overall FRB population, this simulation ignores many observational biases (scattering, observing coverage) and the effects of galaxy evolution, which is likely significant over the range of redshifts to which \frb\ is detectable \citep[e.g.,][]{2010ApJ...709..644I}. The burst energies are estimated from observations from 2.5 to 3.5~GHz, which may be a biased selection of all bursts or may not include all burst emission. If the simulation is revealing a connection between \frb\ and the broader FRB population, it does not explain the physical mechanism that drives it. The burst energy distribution of the population could be dominated by intrinsic or extrinsic effects \citep{2015MNRAS.451.3278M,2016Natur.531..202S,CORDES}. More FRB detections will improve the quality of this inference as sample variance drops, while more burst detetions from \frb\ will improve the measurement of the intrinsic energy distribution.

@@

The chance of detecting a burst with the VLA changes substantially on day--month timescales. A major outstanding question is whether this time-variable rate is driven by an intrinsic process \citep{2016ApJ...826..226K} or extrinsic (propagation) effects \citep{CORDES}. However, the temporal distribution of VLA detections alone shows that \frb\ has significant correlation on short timescales. That is, detecting a burst predicts you are more likely to find another burst soon thereafter and not detecting a burst predicts you will likey not detect another burst soon thereafter. While this is sometimes referred to as a ``red spectrum'' \citep{2016MNRAS.458L..89C}, the observations presented here are only sensitive to timescales of days (time between observations) and months (time between campaigns).

If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}. It is possible that other FRBs have repeating bursts, but calculating a limit requires knowing their temporal correlation function. Wide, shallow surveys are the preferred strategy for blind detection of FRBs. Also, since ``bursts predict bursts'', many short observations are more likely to blindly detect an FRB than a single long observation of the same total length.

@@

\section{Conclusions}

The recent precision localization of \frb\ has helped identify a host galaxy, measure its distance, and establish it as a member of a truly new class of astrophysical source. With its cosmological distance firmly established, \frb\ now serves as a new kind of standard by which FRBs are defined. That fact, combined with an abundance of data collected during its high activity state, allows us to apply this source to more general questions about the FRB population.
